\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-05-03 arch.tex
updates

A prime motivation behind the \rx architecture was to design a
controller which could bring automated planning closer to low-level
control of the vehicle while maintaining its reactivity. Traditionally
planning has been deemed computationally expensive with planner
performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash
\footnote{\kcomment{In such an event as the planner works towards goal
    satisfaction, the initial conditions leading to achieve that goal
    are no longer valid. The planner then tries to achieve a different
    goal which too has to be discarded similarly. And so on.}}  if the
internal state of the plan gets out of sync with the actual state of
the world.

\kcomment{A important consequence of this has been that} the planning
problem managed {\em in situ} has traditionally remained fairly
detached from low-level control. Most adaptations at the lower-level
reactive layers in contrast are managed by specialized components (for
example \texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
with \rx builds on this design methodology albeit in a substantially
systematic manner.

@@

\item \emph{Partitioning} the global planning problem into multiple
  decision loops, called {\em reactors}. Each reactor has its own
  scope both functionally (one for example focusing on the conversion
  of high level waypoints into low-level commands) and temporally as
  each reactor declares its planning look-ahead ($\pi$) and expected
  latency ($\lambda$) before being able to produce \kcomment{a} plan
  to the agent depending on where it is located in a reactor
  dependency graph such as shown in Fig. \ref{fig:agent}. A reactor
  closer to the hardware in the hierarchy, is expected to deliberate
  less and be highly responsive to observations from the world. This
  implies lower values of $\pi$ and $\lambda$ (see Section
  \ref{sec:arch:trex} below). \kcomment{In the current design, $\pi$
    and $\lambda$ are application dependent and fixed at design time.}

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution to ensure that planning occurs
  \emph{during continuous} state update in the {\em same}
  \kcomment{plan} database used for planning. By doing so, the planner
  is better informed in its deliberation despite a larger latency than
  the changing world.
\end{itemize}

Systematic partitioned inference is a major contribution of
\rxe. However that is not the focus of this chapter; details are
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a substantial impact on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to the \rx framework by first
linking concepts in temporal planning with the framework. Note that in
the following treatise, we call the formal semantic framework of \rx
as the 'agent'. Reactors constitute an entity within this agent and
are standalone blocks of inference. The scope, detail and number of
reactors are application specific and outside the scope of this
chapter.

>>>>

A prime motivation behind the \rx architecture was to design a
controller which could bring automated planning closer to low-level
control of the vehicle while \kcomment{ensuring}
reactivity. Traditionally planning has been deemed computationally
expensive with planner performance restricting robot reactivity
\cite{ghallab04,Dias:2003ua}. In control architectures where task
planning is embedded, planning consequently remains at an abstract
level with the assumption that it would otherwise impede system
reactiveness and that the environment can change at a faster rate than
the planner can plan for. In such a situation, the agent may thrash
\footnote{\kcomment{In such an event even as the planner works towards
    goal satisfaction, the initial conditions leading to achieve that
    goal are no longer valid. The planner then tries to achieve a
    different goal which too has to be discarded similarly. And so
    on.}}  if the internal state of the plan gets out of sync with the
actual state of the world.

\kcomment{An important consequence of this has been that} the planning
problem managed {\em in situ} has traditionally remained fairly
detached from low-level control. Most adaptations at the lower-level
reactive layers in contrast are managed by specialized components (for
example \texttt{LAAS architecture} \cite{alami:1998p820,Ingrand07} and
\texttt{CLARATy} \cite{Nesnas:2003do}) that rely on different
representations for modeling local control behavior or worse do not
have any explicit formal agent behavior model. The consequent
different techniques for specifying each layer in the architecture
results in duplication of effort and a diffusion of knowledge leading
to significant design and integration issues \cite{DS1report}.
\texttt{IDEA} mitigated most of these issues by tightly integrating
planning and execution in a single representational and computational
framework with \kcomment{an} unified declarative model. Our approach
builds on this design methodology albeit in a substantially systematic
manner.

@@

\item \emph{Partitioning} the global planning problem into multiple
  decision loops called {\em reactors}. Each reactor has its own scope
  both functionally (one for example focusing on the conversion of
  high level waypoints into low-level commands) and temporally as each
  reactor declares its planning look-ahead ($\pi$) and expected
  latency ($\lambda$) before being able to produce \kcomment{a} plan.
  \kcomment{These parameters depend} on where \kcomment{a reactor} is
  located in a dependency graph such as \kcomment{the one} shown in
  Fig. \ref{fig:agent}. A reactor closer to the hardware in the
  hierarchy, is expected to deliberate less and be highly responsive
  to observations from the world. This implies lower values of $\pi$
  and $\lambda$ (see Section \ref{sec:arch:trex} below). \kcomment{In
    the current design, $\pi$ and $\lambda$ are application dependent
    and fixed at design time.}

\item \emph{Coupling} a tighter integration between the planning
  process and world evolution \kcomment{with the use of the {\em same}
    \kcomment{plan} database}. By doing so, the planner is better
  informed in its deliberation despite a larger latency than the
  changing world.
\end{itemize}

Systematic partitioned inference is a major contribution of
\rxe. However that is not the focus of this chapter with details
covered in \cite{py10, rajan12}. Coupled interaction between planning
and the world on the other hand, has a substantial impact on how
planning can be integrated in such frameworks. In this chapter we show
how using the \eu planner can be coupled to the \rx framework by first
linking concepts in temporal planning with the framework. Note that in
the following treatise, we call the formal semantic framework of \rx
as the 'agent'. Reactors constitute an entity within this agent and
are standalone blocks of inference. The scope, detail and number of
reactors are application specific and outside the scope of this
chapter.
